---
title: "R Notebook"
output: html_notebook
---

```{r setup}
library(readxl)
Book4 <- read_excel("Book4.xlsx", range = "c28:f58")

convertRank = function(val){
  return (rank(val, ties.method = "min"))
}

df = data.frame(
  q1 = convertRank(c(Book4$Q1)),
  q2 = convertRank(c(Book4$Q2)),
  q3 = convertRank(c(Book4$Q3)),
  q4 = convertRank(c(Book4$Q4))
)

drawPlot1 = function(val, clr){
  x = c(1:30)
  
  plot(x, val, ylim=c(0, 30), col=clr)
  par(new=T)
}

makeVector = function(val){
  len = 30
  ret = c()

  for (i in 1:len){
    ret = c(ret, calc(val[i,]))
  }
  
  return(ret)
}

calc = function(p){
  a = 0.85819
  b = 0.07058
  c = -0.00324
  d = 1.03151
  
  return(a*p$q1 + b*p$q2 + c*p$q3 + d)
}

drawPlot2 = function(val){
  x = c(1:30)
  
  plot(x, val, ylim=c(0, 30), col="black", type = "l")
}

```
## convert interval data to rank data
Before
`r Book4`

After
`r df`

## 1. Obtain regression equation
```{r}
ret = lm(df$q4~., data=df)
summary(ret)
```

## 2. Evaluate effectiveness of equation and significance of regression coefficients
```{r}
drawPlot1(df$q1, "red")
drawPlot1(df$q2, "green")
drawPlot1(df$q3, "blue")
drawPlot1(df$q4, "black")
drawPlot2(makeVector(df))
```

## 3. What can you say from cause-effect analysis?(what would give larger impact to overall satisfaction)?
Mutiple R-squared is 97%.  This model is trustable.  

Q1 P value is less than 5%.  
Q1 (contents of class) has positive impact to overall satisfuction.  

Other P values are more than 5%.  
Q2 (understanding of contents) has almost no impact to overall satisfuction.  
Q3 (educational facilities) has almost no impact to to overall satisfuction.